% rtc-resume.tex
\documentclass[11pt]{moderncv}

\moderncvstyle{classic}
\moderncvcolor{purple}
\definecolor{color1}{RGB}{212,138,213}
\usepackage[utf8]{inputenc}
\usepackage{tgschola}
\usepackage[T1]{fontenc}
\usepackage[left=.5in,right=.5in,top=.5in,bottom=.5in,letterpaper]{geometry}

\firstname{\textsc{Rachael}}
\familyname{\textsc{Carlson}}
\address{3308 N. Bremen St.}{Milwaukee, WI 53212}
\phone{(612) 616-4422}
\email{rtc@sleeplimited.org}
\homepage{rachaelcarlson.us}
% \homepage{sleeplimited.org}
\begin{document}

\makecvtitle
\section{\textsc{Objective}}
\cvline{}{\textbf{To improve my skills in Fingerstyle Guitar performance, transcription, and typesetting through music scholarship and performance}}
% \cvline{}{\textbf{Use my administrative and interpersonal skills to support
% Milwaukee public services}}

\section{\textsc{Education}}
\cventry{May 2013}{Master's of Liberal Studies}{University of
Wisconsin-Milwaukee}{Milwaukee, WI}{\textit{3.9/4.0}}{Chancellor's
Award: Scholarship for Graduate Studies}
\cventry{May 2011}{Bachelor's of Fine Arts}{University of
Wisconsin-Milwaukee}{Milwaukee, WI}{\textit{3.5/4.0}}{}
\cventry{May 2011}{Rock and Roll Studies Certificate}{University of
Wisconsin-Milwaukee}{Milwaukee, WI}{}{Coordinator: Dr. Martin Jack Rosenblum}

\section{\textsc{Master's Thesis}}
 \cvline{Title}{\emph{Visions of \emph{Blonde on Blonde}: Toward a
 Foundation of Rock and Roll Criticism}}
 \cvline{Supervisor}{Dr. Martin Jack Rosenblum}
 \cvline{Description}{\small \emph{Blonde on Blonde} by Bob Dylan
 contains some of the earliest examples of the complex narrative in
 popular music; this complex narrative changes the way that Popular
 Music Studies works with Pop music and a critical study of its
 contents needs to be started.  This paper provides a theoretical
 foundation of New Criticism, Semiotics, and Jungian Criticism upon
 which a critical canon of the complex narrative can built.}


\section{\textsc{Publications and Recordings}}
 \cvline{Bibliographer}{\emph{Searching for Rock and Roll}.  Martin
 Jack Rosenblum and David Luhrssen.  CengageLearning: Mason, 2012.
 Fourth Edition.  978-0-495-99152-6}
 \cvline{Composer, Musician}{\emph{Remove the
 Believer} by SUN ROCK MAN.  \url{http://www.cdbaby.com/cd/sunrockman}}

\section{\textsc{Performance Experience}}
 \cvline{Fingerstyle Guitar}{Hundreds of solo performances at locations such as: The Milwaukee Public Market, The Milwaukee Art Museum, wedding ceremonies, and Milwaukee Cafes and Bars.}
 \cvline{}{Performances in master classes with musicians such as: Pierre Bensusan, Alex DeGrassi, The Venere Lute Quartet, Ronn MacFarlane, and Andy McKee.}
 \cvline{}{Performances in ensemble environments with The Milwaukee Mandolin Orchestra, Camerata Milwaukee, the UW-Milwaukee Guitar Orchestra, and small chamber groups performing early and contemporary music.  Also founded, recorded with, and performed in the progressive rock band SUN ROCK MAN.}
% \section{Experience}
% \cventry{2010-Current}{Archivist, Bibliographer, and Office
% Manager}{Spiritfugitive, LLC}{}{}{\begin{itemize}
%     \item Analyze and disseminate thousands of documents and media
%         related to American Free Verse Poetry History 
%     \item Compile extensive discography, filmography, and bibliography
%         for textbook published by a major academic publisher on the
%         subject of American oral tradition music
%     \item Communicate orally and in writing with numerous libraries,
%         publishers, and record labels
% \end{itemize}
% }
% \cventry{2008-2013}{Library Assistant}{University of
%     Wisconsin-Milwaukee Golda Meir Music \& Curriculum
% Libraries}{}{}{\begin{itemize}
%     \item Provide reference and circulation services in Music \&
%         Curriculum sujbect areas through in-person, telephone, and online
%         methods for thousands of patrons 
%     \item Organize and maintain the efficiency of all office related
%         activities
%     \item Digitize sound materials for patron and archive usage 
%     \item Maintain and update the Music Library website with skills
%         learned on site 
%     \item Operate sound and presentation equipment for classroom purposes
% \end{itemize}
% }
% \cventry{2011-2012}{Assistant Teacher}{University of
% Wisconsin-Milwaukee}{}{}{\begin{itemize}
%     \item Lecture on the subject of American Folk and Popular music
%         emphasizing historical perspective and lyrical development
%     \item Develop engaging and relevant curriculum within the subject
%         of Rock and Roll and its literary aspects
%     \item Support classroom technologies and facilities to increase
%         classroom operations efficiency
%     \item Assist the other instructor with lesson plans on the subject
%         of American Vernacular and Popular music
% \end{itemize}
% }

% \section{Volunteer Experience}
% \cventry{2008-present}{Volunteer}{Riverwest Co-op Grocery \&
% Cafe}{Human Resources \& Inclusion Committees}{}{\begin{itemize}
%     \item Implement a new and cohesive form for meeting minutes which
%         ensures accountability and efficiency 
%     \item Write minutes for each meeting, ensuring accuracy and action items
%         are addressed
%     \item Ensure that each employee is receiving the proper amount of money for
%         each paycheck
%     \item Organize Anti-Discrimination training for Board and Staff 
%     \item Participate in various sub-committees that deal with hiring,
%         customer service, and policy revision, creation, and enactment
% \end{itemize}
% }

\section{\textsc{References Available Upon Request}}


\end{document}
